High-Dimensional Regularized Discriminant Analysis

### 2016-01-30 reports/paper-hdrda.Rnw
Added link to GitHub repo. Closes #24

\usepackage{graphicx, amsmath, amssymb, bm, mathtools, amsthm, natbib, setspace, algorithm2e, authblk}

@@

In this section, we compare our proposed classifier with four classifiers
recently proposed for small-sample, high-dimensional data along with the
random-forest classifier from \cite{Breiman:2001fb} using version 3.2.2 of the
open-source statistical software {\tt R}. Within our study, we included
penalized linear discriminant analysis from \cite{Witten:2011kc}, implemented in
the {\tt penalizedLDA} package. We also considered shrunken centroids
regularized discriminant analysis from \cite{Guo:2007te} in the {\tt rda}
package. Because the {\tt rda} package does not perform the authors' ``Min-Min''
rule automatically, we applied this rule within our {\tt R} code. We included
two modifications of diagonal linear discriminant analysis from
\cite{Tong:2012hw} and \cite{Pang:2009ik}, where the former employs an improved
mean estimator and the latter utilizes an improved variance estimator. Both
classifiers are available in the {\tt sparsediscrim} package. Finally, we
incorporated the random forest as a benchmark based on the findings of
\cite{FernandezDelgado:2014ul}, who concluded that the random forest is often
superior to other classifiers in benchmark studies. We used the implementation
of the random-forest classifier from the {\tt randomForest} package with 250
trees and 100 maximum nodes. For each classifer we explicitly set prior
probabilities as equal, if applicable. All other classifier options were set to
their default settings. Below, we refer to each classifier by the first author's
surname. All simulations were conducted on an Amazon Elastic Compute Cloud (EC2)
{\tt c4.4xlarge} instance.

>>>>

\usepackage{graphicx, amsmath, amssymb, bm, mathtools, amsthm, natbib, setspace}
\usepackage{algorithm2e, authblk, url}

@@

In this section, we compare our proposed classifier with four classifiers
recently proposed for small-sample, high-dimensional data along with the
random-forest classifier from \cite{Breiman:2001fb} using version 3.2.2 of the
open-source statistical software {\tt R}. Within our study, we included
penalized linear discriminant analysis from \cite{Witten:2011kc}, implemented in
the {\tt penalizedLDA} package. We also considered shrunken centroids
regularized discriminant analysis from \cite{Guo:2007te} in the {\tt rda}
package. Because the {\tt rda} package does not perform the authors' ``Min-Min''
rule automatically, we applied this rule within our {\tt R} code. We included
two modifications of diagonal linear discriminant analysis from
\cite{Tong:2012hw} and \cite{Pang:2009ik}, where the former employs an improved
mean estimator and the latter utilizes an improved variance estimator. Both
classifiers are available in the {\tt sparsediscrim} package. Finally, we
incorporated the random forest as a benchmark based on the findings of
\cite{FernandezDelgado:2014ul}, who concluded that the random forest is often
superior to other classifiers in benchmark studies. We used the implementation
of the random-forest classifier from the {\tt randomForest} package with 250
trees and 100 maximum nodes. For each classifer we explicitly set prior
probabilities as equal, if applicable. All other classifier options were set to
their default settings. Below, we refer to each classifier by the first author's
surname. All simulations were conducted on an Amazon Elastic Compute Cloud (EC2)
{\tt c4.4xlarge} instance. Our analyses can be reproduced using the code
available in the \url{https://github.com/ramhiser/paper-hdrda} repository.
